%-------------------------------------------------------------------------------
%   SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%   CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Director of Engineering} % Job title
    {Airware} % Organization
    {Paris, San Francisco} % Location
    {Sep. 2016 - Ongoing} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Support the transformation of a French startup into a multi national company.}
        \item {Primary responsibilities:}
        \begin{cvsubitems}
          \item {Product Management, Datascience and Machine Learning Roadmap definition,}
          \item {Platform architecture,}
          \item {Engineers managers,}
        \end{cvsubitems}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Advanced Machine Learning projects live in production,}
          \item {Architecture principles I defined at Redbird are now embrassed at the global level.}
        \end{cvsubitems}
        \item {Lessons learnt:}
        \begin{cvsubitems}
          \item {Machine Learning applications are more than wide. We have just scratch the surface of their capabilities,}
          \item {Cloud native services definitely empower development teams to do more with less.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Vice President of Engineering} % Job title
    {Redbird} % Organization
    {Paris} % Location
    {Jan. 2016 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Transform an MVP into a viable and valued product, developing advanced partnership and new features for our industries.}
        \item {Primary responsibilities:} % Turning business vision into actionable technical strategy
        \begin{cvsubitems}
          \item {Architecture and Roadmap definition,}
          \item {Product Management (customer requirements analyze, product specification, feature prioritization),}
          \item {3rd parties module implementation with business partners,}
          \item {Team onboarding on AWS cloud services: from traditionnal databases and workloads to more advanced serverless services.}
        \end{cvsubitems}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Best in class architecture focused on high-availability, fault tolerance, and auto-scaling,}
          \item {1st serverless RESTfull API implementation, Setup of all of our AWS services before training of the team,}
          \item {Airware Acquisition Due Diligence,}
          \item {AWS Selection at the Startup corner for Paris Summit.}
        \end{cvsubitems}
        \item {Lessons learnt:}
        \begin{cvsubitems}
          \item {More operational and developments activities suit me well,}
          \item {Working with cutting-edge technologies that may have never been used in the field is more than thrilling,}
          \item {Problem understanding and solving in creative ways is at the root of my professional skills.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Manager} % Job title
    {Accenture, Innovation lead for Resource France} % Organization
    {Paris Area} % Location
    {Jul. 2015 - Jan. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Definition of an Innovation program for Resource France.}
        \item {Primary responsibilities:}
        \begin{cvsubitems}
          \item {Open Innovation Champion: screening startups with potential and carefuly classifying them,}
          \item {Paris Innovation Hub Champion: innovation offering definition and in field experience, trainings testing and definition.}
        \end{cvsubitems}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Definition of transformation program for Innovation @ Resources France,}
          \item {Resources people acculturation and Network animation,}
          \item {Workshops setup \& execution, Built a 20+ opportunities pipe,}
          \item {Screened 10+ serious startup for future Accenture proposales,}
          \item {``Paris Innovation Hub" service and physical space definitions.}
        \end{cvsubitems}
        \item {Lessons learnt:}
        \begin{cvsubitems}
          \item {All aspects of innovation thrill me,}
          \item {Train and experienced UX design, design thinking, lean startup, business model canvas.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Manager} % Job title
    {Accenture, for GRTgaz} % Organization
    {Paris Area} % Location
    {May 2012 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scope: 10+ applications program management (best of breed technologies), 60+ FTE on average (120+ max), 2 delivery centers (Nantes and Mumbai).}
        \item {Technologies: Oracle Database, Oracle Lodestar, Webmethods, J2EE, HTML 5, Selligent, Informatica, Mobile, Nagios, PHP, etc.}
        \item {Business Perimeter: Capacities Booking, Nominations, Services, Capacity product creation and offering, Pricing, Measure, allocation and Services management, Meter referential, CRM, Allocation, billing \& invoicing, Gas quality analysis and simulation, Business processes supervision, Publication and alert processing.}
        \item {Primary responsibilities:}
        \begin{cvsubitems}
          \item {Program lead (transitions, finances, quality assurance, risk), }
          \item {Opportunities development, scope expension,}
        \end{cvsubitems}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Transition of various applications from a set of different sub-contractors,}
          \item {Transition of activities from Paris to delivery centers - near shore (Nantes) and offshore (Mumbai, India),}
          \item {Different activity types: Application Outsourcing, Application Delivery, Proof of Concepts developments, Infrastructure Outsourcing,}
          \item {AWS cloud implementation: development and staging environments,}
          \item {Financial success thanks to industrialization, management optimization, reorganization \& cost rationalization,}
          \item {20000+ man.days delivered on time, Hundreds of release,}
          \item {98\%+ green SLAs \& close to 0\% revenue penalties.}
        \end{cvsubitems}
        \item {Lessons learnt:}
        \begin{cvsubitems}
          \item {Managing large teams in 3 different offices, different time zones, including 2 delivery centers in 2 languages,}
          \item {Process industrialization and well-balanced mix of Technical and Consulting profiles are mandatory for large programs,}
          \item {Large delivery is interesting but it involves repetitive tasks I want to avoid in the future,}
          \item {Cloud is disruptive, it enables new use cases, enable creativity with a major drawback: it requires additional and strong cost controls.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant} % Job title
    {Accenture, for GDF Suez} % Organization
    {Paris Area} % Location
    {Nov. 2009 - Sep. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scope: different architecture solutions studies}
        \item {Primary responsibilities:}
        \begin{cvsubitems}
          \item {Part of GDF Suez architecture team and counsil,}
          \item {Researchs and writing of solutions involving all impacted teams,}
          \item {Architectures and Roadmaps definitions and scenario sizing and scheduling.}
        \end{cvsubitems}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Definition of an application responsible for energy consumption and optimization of end users consumers,}
          \item {Definition of architecture scenarios (accounting for different budget, schedules and impacts on all impacted projects),}
          \item {Writing of a weighing architecture document for company counsil for the replacement of SAP and Selligent with Salesforce.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Consultant} % Job title
    {Accenture, for GDF Suez} % Organization
    {Paris Area} % Location
    {Jan. 2009 - Sep. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scope: SAP IS-U / CRM utilities information system. 10 million customers, 3 thousand users, 40 million bills a year.}
        \item {Primary responsibilities:}
        \begin{cvsubitems}
          \item {Integrated to the GDF Suez team,}
          \item {Product manager: high level business requirements gathering, solution design, sizing, general design document writing,}
          \item {Support and monitoring of all down-stream teams,}
        \end{cvsubitems}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Business requirements analyses, solution sizing, and developments on various features: Price determination, CRM, Meter Reading and Integration, Consumption Extrapolation, Billing and Invoicing, Budget Billing Plan Subscription,}
          \item {Proof of Concept implementation of a new dunning system based on latest SAP features, setting the way for years to come,}
          \item {Design of a machine-machine solution solving all the previous issues and accounting for future needs,}
          \item {Implementation of an Invoice automatic validation tools - still in use years after I lived, saving thousands hour of manual,}
          \item {Definition and delivery of a new machine-machine interface that replaces the historical one: Smart meters compatible, Fully customizable,}
          \item {Utilities vulgarization and Accenture Resource team training.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Analyst} % Job title
    {Accenture, for Gaz De France} % Organization
    {Paris Area} % Location
    {Jan. 2007 - Dec. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scope: SAP IS-U / CRM utilities information system. 10 million customers, 3 thousand users, 40 million bills a year.}
        \item {Primary responsibilities:}
        \begin{cvsubitems}
          \item {Functional and technical requirements analyze, Solution design and costs determination}
          \item {Planning, redaction and execution of assembly, product, performance and user acceptance tests,}
          \item {Monitoring and support of 60+ interfaces,}
          \item {Applicartion Maintenance.}
        \end{cvsubitems}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Multiple application designs and implementations related to machine-machine interfaces, pricing, billing and invoicing,}
          \item {Improvement of machine-machine integration tests thanks to active and extensive actions follow up across numerous entities,}
          \item {Maintenance of production workloads, emergency solving,}
          \item {Expertise development,}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web developer} % Job title
    {Arcorp, Idoine, Satis (Web agency and software editor)} % Organization
    {Paris} % Location
    {Sep. 2005 - Dec. 2005} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a web application in Java/J2EE for the FSE (Fonds Social Européen).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
