%-------------------------------------------------------------------------------
%   SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activities}


%-------------------------------------------------------------------------------
%   CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Manager @ Accenture} % Job title
    {Video \& Image Analytics Service (Intrapreuneurship experience)} % Organization
    {Paris Area} % Location
    {Dec. 2013 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scope: Definition of a potential partnership with drone operators and service providers.}
        \item {Primary responsibilities:}
        \begin{cvsubitems}
          \item {Business model definition,}
          \item {Business plan writing,}
          \item {Leveraging Accenture Internal capabilities (including labs in France and San Jose),}
          \item {Partnership creation and nourishing,}
          \item {Presentation to a board of industries lead directors.}
        \end{cvsubitems}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Implementation of a proof of concept that demonstrate scalability of drone operations leveraging GPU in the cloud,}
          \item {Platform prototypes (involging User Experience of real life use case),}
          \item {Business Plan,}
          \item {Innovation award.}
        \end{cvsubitems}
        \item {Lessons learnt:}
        \begin{cvsubitems}
          \item {Innovation thrills me,}
          \item {Never doing the same thing is key to me,}
          \item {Ability to deal with any technology in a lot of different contexts.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer iOS} % Job title
    {Purring Box (Mobile Application)} % Organization
    {Paris Area} % Location
    {Jan. 2009 - Dec. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scope: iOS smartphone application development. Purring therapy applied to mobile application.}
        \item {Primary responsibilities: product definition, product design and roadmap, application development and deployment}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Product definition and design,}
          \item {Product development,}
          \item {Product deployment,}
          \item {Enough downloads to pay Apple development membership for years.}
        \end{cvsubitems}
        \item {Lessons learnt:}
        \begin{cvsubitems}
          \item {Incredibly easy to learn Objective-C and the entire iOS eco-system,}
          \item {1st version Application development was light fast,}
          \item {Getting an application to be known is the hardest piece of the story.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teacher Assistant, tutor (YAKA, ACU)} % Job title
    {EPITA} % Organization
    {Paris} % Location
    {Jan. 2006 - Aug. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Primary responsabilities: In charge of practical courses and lectures.}
        \item {Scope: Object Oriented Languages, Imperative programming, Scripting, Design, Design Patterns, UNIX, network.}
        \item {20 Teacher Assistants / 300 students}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web developer} % Job title
    {EPITA} % Organization
    {Paris} % Location
    {Jan. 2006 - Aug. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scope and primary responsabilities: internationalization of a social web site that manages ideas and initiatives development related to ecology and environment saving using taxonomy principle. Requirement gathering and solution design.}
        \item {Entity: SWOORD, Save WOrld frOm Read Disaster.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
