%-------------------------------------------------------------------------------
%   SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activities}


%-------------------------------------------------------------------------------
%   CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Manager @Accenture} % Job title
    {Video \& Image Analytics Service (Intrapreuneurship experience)} % Organization
    {Paris Area} % Location
    {Dec. 2013 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Definition of business plan where Accenture was partnering with a French drone operator and service provider.}
        \item {Primary responsibilities:}
        \begin{cvsubitems}
          \item {Business model definition,}
          \item {Business plan writing,}
          \item {Leveraging Accenture Internal capabilities (including labs in France and San Jose),}
          \item {Partnership creation and nourishing,}
          \item {Presentation to a board of industries lead directors.}
        \end{cvsubitems}
        \item {Major tasks accomplished:}
        \begin{cvsubitems}
          \item {Implementation of a proof of concept that demonstrate scalability of drone operations leveraging GPU in the cloud,}
          \item {Platform prototypes (involging User Experience of real life use case),}
          \item {Business Plan,}
          \item {Innovation award.}
        \end{cvsubitems}
        \item {Lessons learnt:}
        \begin{cvsubitems}
          \item {Innovation thrills me,}
          \item {Never doing the same thing is key to me,}
          \item {Ability to deal with any technology in a lot of different contexts.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer iOS} % Job title
    {Purring Box (Mobile Application)} % Organization
    {Paris Area} % Location
    {Jan. 2009 - Dec. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Product definition, design, development and deployment of a mobile application that leverages purring therapy.}
        \item {Lessons learnt:}
        \begin{cvsubitems}
          \item {Incredibly easy to learn a new language and eco-system: 1st version Application developement was light fast,}
          \item {Getting an application to be known is the hardest piece of the story.}
        \end{cvsubitems}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teacher Assistant (20 tutors / 300 students), Web developer} % Job title
    {EPITA} % Organization
    {Paris} % Location
    {Jan. 2006 - Aug. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In charge of practical courses and lectures (Object Oriented Languages, Scripting, Design \& Design Pattersn, Unix).}
        \item {Internationalization of a social web site that manages ideas and initiatives development related to ecology and environment saving.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
